---
title: "Bibliometric Analysis"
author: "Pablo Coello Pulido"
date: "22/2/2020"
output: html_document
params:
  file: scopus.bib
  path: ~/GitHub/data/bibliometrics
  k: 10
---
# Bibliometric analysis of specific keywords

```{r Load librarys, echo=FALSE, comment='', message=FALSE, warning=FALSE}
if(!require(readxl)){install.packages("readxl");library(readxl)}
if(!require(dplyr)){install.packages("dplyr");library(dplyr)}
if(!require(tidyr)){install.packages("tidyr");library(tidyr)}
if(!require(stringr)){install.packages("stringr");library(stringr)}
if(!require(bibliometrix)){install.packages("bibliometrix");library(bibliometrix)}
if(!require(xml2)){install.packages("xml2", dependencies=TRUE, INSTALL_opts = c('--no-lock'));library(xml2)}
#https://github.com/massimoaria/bibliometrix
if(!require(quanteda)){install.packages("quanteda");library(quanteda)}
if(!require(ggplot2)){install.packages("ggplot2");library(ggplot2)}
if(!require(lubridate)){install.packages("lubridate");library(lubridate)}
if(!require(sf)){install.packages("sf");library(sf)} 
```

Todo el proceso explicado (más o menos) aquí: http://htmlpreview.github.io/?https://github.com/massimoaria/bibliometrix/master/vignettes/bibliometrix-vignette.html


```{r load data, message=FALSE, warning=FALSE, include=FALSE}
setwd(params$path)
bib <- readFiles(params$file)
M <- convert2df(bib, dbsource = "scopus", format = "bibtex")

wd<-(paste(params$path, '/geo_data', sep=''))
setwd(wd)
shp <- read_sf(dsn = paste(wd,"", sep=""), 
               layer = "geo_data")
```



```{r perform sumary, message=FALSE, warning=FALSE, include=FALSE}
results <- biblioAnalysis(M, sep = ";")
S <- summary(object = results, k = params$k, pause = FALSE)

knitr::kable(
  S[1]
)
```

# Overall stats
```{r overall table, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[2]
)
```
## Yearly production

```{r Year production, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[3]
)
```

## Articles per author (most productive authors)

```{r Principal authors and articles, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[5]
)
```
## Total citations most citated authors

```{r Main articles, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[6]
)
```
## Articles per country

```{r production per country, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[7]
)
```
## Citations per country
```{r Citations per country, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[8]
)
```
## Main sources
```{r main topics, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[9]
)
```

## Main keywords
```{r main keywords, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(
  S[10]
)
```



## Descriptive plots

```{r temporal plots, echo=FALSE, message=FALSE, warning=FALSE}
plot(x = results, k = params$k, pause = FALSE)
```

```{r geo plot, echo=FALSE, message=FALSE, warning=FALSE}
geo_plot <- S$MostProdCountries
shp$NAME <- toupper(shp$NAME)
shp[154,'NAME'] <- 'USA'


shp$Articles <- 0
for (country in gsub(' ','',shp$NAME)){
  if (country %in% gsub(' ','',geo_plot$Country)){
    shp[which(gsub(' ','',shp$NAME)==country),'Articles'] = geo_plot[which(gsub(' ','',geo_plot$Country)==country),"Articles"]
  }
}

shp$Articles = as.numeric(shp$Articles)
ggplot(shp %>% filter(Articles != "NA")) +
  geom_sf(aes(fill = Articles)) 
```


## Top citations

In this table we can see the top citated articles by the references included in our analysis.

```{r top citations, echo=FALSE, message=FALSE, warning=FALSE}
CR <- citations(M, field = "article", sep = ";")

knitr::kable(
  cbind(CR$Cited[1:10])
)
```


## Top citated authors

Top citatedd authors by the references included in our analysis.
```{r top citated authors, echo=FALSE, message=FALSE, warning=FALSE}
CR <- citations(M, field = "author", sep = ";")
knitr::kable(
  cbind(CR$Cited[1:10])
)
```

## Dominance ranking

```{r dominance ranking, echo=FALSE, message=FALSE, warning=FALSE}
DF <- dominance(results, k = params$k)

knitr::kable(
  DF
)
```


### H index for the 10 most productive authors

```{r h 10 most productive, echo=FALSE, message=FALSE, warning=FALSE}
authors=gsub(","," ",names(results$Authors)[1:params$k])

indices <- Hindex(M, field = "author", elements=authors, sep = ";", years = 50)
knitr::kable(
  indices$H
)
```

## Top autors productivity over time

```{r authors productivity over time, echo=FALSE, message=FALSE, warning=FALSE}
topAU <- authorProdOverTime(M, k = params$k, graph = TRUE)
```


## Lotka`s coefficient

```{r Lotka`s coefficient, echo=FALSE, message=FALSE, warning=FALSE}
L <- lotka(results)

# Author Productivity. Empirical Distribution
knitr::kable(
  L$AuthorProd
)
```


## Network analysis

### Authors co-citation network

```{r coupling network, echo=FALSE, message=FALSE, warning=FALSE}
NetMatrix <- biblioNetwork(M, analysis = "coupling", network = "authors", sep = ";")
net=networkPlot(NetMatrix, normalize = "salton", weighted=T, n = 20, labelsize=0.5,curved=TRUE,Title = "A Co-citation Network of Authors", type = "kamada", size=TRUE,remove.multiple=TRUE)
```

```{r network stats, echo=FALSE, message=FALSE, warning=FALSE, comment=""}
netstat <- networkStat(NetMatrix)
summary(netstat, k=params$k)

```


## Country scientific collaboration

```{r countries network, echo=FALSE, message=FALSE, warning=FALSE}

M <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "collaboration", network = "countries", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = dim(NetMatrix)[1], Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE,labelsize=0.7,cluster="none")
```


## Articles co-citation network

```{r Co-citation network, echo=FALSE, message=FALSE, warning=FALSE}

NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = 30, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)
```


## Keywords co-ocurrences network
```{r co-ocurrences network, echo=FALSE, message=FALSE, warning=FALSE}
# Create keyword co-occurrences network

NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```

# Conceptual structure using keywords
```{r Conceptual structure, echo=FALSE, message=FALSE, warning=FALSE}
# Conceptual Structure using keywords (method="CA")

CS <- conceptualStructure(M,field="TI", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=5, documents=5)
```

```{r historical network, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Create a historical citation network
options(width=130)
histResults <- histNetwork(M, min.citations = 10, sep = ";")
```


```{r network result, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
net <- histPlot(histResults, n=15, size = 10, labelsize=5)
```


